### 2018-12-28 taco/tex/optimization.tex
Add taco

\section{Shuffle Optimization}
\label{opt}
This section presents the detailed methodologies to achieve the three design goals. 
The out-of-framework shuffle data management is used to decouple shuffle from execution and provide a cross-framework optimization. 
Two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) and a co-scheduler is used to achieve shuffle data pre-fetching without launching tasks.
\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{fig/reduce_cdf}
	\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
	\label{fig:cdf}
	\vspace{-1em}
\end{figure}
\subsection{Decouple Shuffle from Execution}
% \ifrevision
% \reversemarginpar
% \marginpar{B1,C2}
% \fi
To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
% During shuffle write of map tasks, the partitioned shuffle data blocks will be written on the disks.
% Each block contains a part of input data of a particular reduce task. 
To prevent the release of a slot being blocked by shuffle write,  
SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
After the memory copy, the slot will be released immediately.

From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
With the precondition of shuffle data pre-fetching, 
the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
% Instead, the original implementation of shuffle read will trigger an all-to-all network transfer that keeps CPU idle.
%To this end, all I/O operations are managed outside of the DAG framework, and the slot is occupied only by the CPU intensive phases of task.
\subsection{Pre-schedule with Application Context}
The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
Once the tasks are scheduled, the slots will be occupied to launch them. 
On the other hand, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling. 
% We explore several pre-scheduling schemes in different scenarios, and evaluate the performance calculating the improvement of reduce tasks completion time with trace of OpenCloud \cite{opencloudtrace}. We first emulate the scheduling algorithm of Spark to schedule the reduce tasks of one job, and take the bottleneck of the task set as the completion time. Then we remove the shuffle read time as the assumption of shuffle data pre-fetch and emulate under different schemes. The result is shown in \ref{fig:sim}.
% \begin{figure*}
% 	\centering
% 	\begin{minipage}{0.34\linewidth}
% 		\begin{figure}[H]
% 			\includegraphics[width=\textwidth]{fig/shuffle_size}
% 			\caption{Shuffle Size Comparing with Input Size}
% 			\label{fig:shuffle_size}
% 		\end{figure}
% 	\end{minipage}
% 	\begin{minipage}{0.65\linewidth}
% 		\begin{figure}[H]
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/reduce_cdf}
% 				\caption{Shuffle Time Fraction CDF}
% 				\label{fig:cdf}
% 			\end{subfigure}	
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/sim}
% 				\caption{Stage Completion Time Improvement}
% 				\label{fig:sim}
% 			\end{subfigure}	
% 			\caption{Emulate Result of OpenCloud Trace}
% 		\end{figure}
% 	\end{minipage}
% \end{figure*}
% \begin{figure}
\subsubsection{Problem of Random Mapping}\label{randomassign}
The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
The average shuffle read time is $3.2\%$ of total reduce completion time.
\begin{figure}
	\centering
	\includegraphics[width=0.66\linewidth]{fig/sim}
	\caption{Stage Completion Time Improvement of OpenCloud Trace}
	\label{fig:sim}
	\vspace{-1em}
\end{figure}
As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
We then remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
This is because that data skew commonly exists in data-parallel computing \cite{skewtune, reining, gufler2012load}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{fig/shuffle}
	\caption{Shuffle Data Prediction}
	\label{fig:shuffle}
	\vspace{-1em}
\end{figure}
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/hash_pre}
		\caption{Linear Regression Prediction of Hash Partitioner}
		\label{fig:hash_pre}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
		\label{fig:range_pre_sample}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	\vspace{-1em}
\end{figure*}

@@

@@

For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node 
and applies the longest processing time rule (LPT) \cite{design} to achieve $4/3\text{-}approximation$ optimum. 
Since the sizes of tasks are considered while scheduling, Heuristic MinHeap can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that Heuristic MinHeap has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
% After the scheduling, the completion time of reduce stage is close to the optimal. \textcolor{red}{may need to add math prove between this and optimal}.
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
% The closer $prob$ is to $1/m$, the more evenly this reduce partition is produced in cluster.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
% We set maximum $upper\_bound$ of performance degradation equals to 10\% that can be traded for locality (in extreme skew scenarios).
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$. 
\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx-1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		% \Comment{$m$ is the number of input data}
		% \Comment{$r$ is partition number of reduces}
		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
		% \Comment{$c$ is $r*m$ array of composition data}
		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.
		\State Return if it is impossible.
		% \State $reduces \gets M\left[reduce.host\_id\right].reduce$	
		% \State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
		% \State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
		% \State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
		% \State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
		% \If{$size\_host\leq upper\_bound$ \textbf{and} \\
		% 	\qquad \; $size\_assigned\leq upper\_bound$}
		% 	\State Swap $candidates$ and $reduce$
		% 	\State Update $size$ in $M$
		% 	\State Update $assigned\_host$ in $candidates$ and $reduce$
		% \EndIf
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Accumulated Heuristic Scheduling for Multi-Shuffles}
\label{mhminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
		\State $m\gets$ partition number of map tasks
		\Comment \emph{shuffles} are the previous schedule result 
		\ForAll{$r$ in $p\_reduces$}
			\State $r.size \mathrel{+}= \text{\emph{shuffles}}\left[r.rid\right].size$
			\State $new\_prob\gets \text{\emph{shuffles}}\left[r.rid\right].size / r.size$
			\If{$new\_prob\geq r.prob$}
				\State $r.prob\gets new\_prob$
				\State $r.host\_id\gets \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$
			\EndIf
		\EndFor
		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
		\ForAll{$host\_id$ in $M$}
			\Comment Re-shuffle
			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
				\If{$host\neq \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$}
				\State Re-shuffle data to $host$
				\State $\text{\emph{shuffles}}\left[r.rid\right].assigned\_host\gets host$
				\EndIf
			\EndFor
		\EndFor
		\Return $M$
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}
\subsubsection{Cope with Multiple Shuffle Dependencies}
% \ifrevision
% \marginpar{E5}
% \fi
A reduce stage can have more than one shuffle dependencies in the current DAG computing frameworks. 
The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
For those pending shuffles, it is impossible to predict their sizes. 
This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
But doing this introduces large overhead such as extra task serialization. 
To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.

@@

>>>>

\section{Shuffle Optimization}
\label{opt}
This section presents the detailed methodologies to achieve the three design goals. 
The out-of-framework shuffle data management is used to decouple shuffle from execution and provide a cross-framework optimization. 
Two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) and a co-scheduler is used to achieve shuffle data pre-fetching without launching tasks.

\begin{figure}
    \centering
    \begin{minipage}{0.42\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{fig/reduce_cdf} % first figure itself
		\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
		\label{fig:cdf}
    \end{minipage}\hfill
    \begin{minipage}{0.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{fig/sim} % second figure itself
		\caption{Stage Completion Time Improvement of OpenCloud Trace}
		\label{fig:sim}
    \end{minipage}
\end{figure}

% \begin{figure}
% 	\centering
% 	\includegraphics[width=0.45\linewidth]{fig/reduce_cdf}
% 	\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
% 	\label{fig:cdf}
% 	\vspace{10em}
% \end{figure}

% \begin{figure}
% 	\centering
% 	\includegraphics[width=0.4\linewidth]{fig/sim}
% 	\caption{Stage Completion Time Improvement of OpenCloud Trace}
% 	\label{fig:sim}
% 	\vspace{-1em}
% \end{figure}

\subsection{Decouple Shuffle from Execution}
% \ifrevision
% \reversemarginpar
% \marginpar{B1,C2}
% \fi
To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
% During shuffle write of map tasks, the partitioned shuffle data blocks will be written on the disks.
% Each block contains a part of input data of a particular reduce task. 
To prevent the release of a slot being blocked by shuffle write,  
SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
After the memory copy, the slot will be released immediately.

From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
With the precondition of shuffle data pre-fetching, 
the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
% Instead, the original implementation of shuffle read will trigger an all-to-all network transfer that keeps CPU idle.
%To this end, all I/O operations are managed outside of the DAG framework, and the slot is occupied only by the CPU intensive phases of task.
\subsection{Pre-schedule with Application Context}
The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
Once the tasks are scheduled, the slots will be occupied to launch them. 
On the other hand, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling. 
% We explore several pre-scheduling schemes in different scenarios, and evaluate the performance calculating the improvement of reduce tasks completion time with trace of OpenCloud \cite{opencloudtrace}. We first emulate the scheduling algorithm of Spark to schedule the reduce tasks of one job, and take the bottleneck of the task set as the completion time. Then we remove the shuffle read time as the assumption of shuffle data pre-fetch and emulate under different schemes. The result is shown in \ref{fig:sim}.
% \begin{figure*}
% 	\centering
% 	\begin{minipage}{0.34\linewidth}
% 		\begin{figure}[H]
% 			\includegraphics[width=\textwidth]{fig/shuffle_size}
% 			\caption{Shuffle Size Comparing with Input Size}
% 			\label{fig:shuffle_size}
% 		\end{figure}
% 	\end{minipage}
% 	\begin{minipage}{0.65\linewidth}
% 		\begin{figure}[H]
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/reduce_cdf}
% 				\caption{Shuffle Time Fraction CDF}
% 				\label{fig:cdf}
% 			\end{subfigure}	
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/sim}
% 				\caption{Stage Completion Time Improvement}
% 				\label{fig:sim}
% 			\end{subfigure}	
% 			\caption{Emulate Result of OpenCloud Trace}
% 		\end{figure}
% 	\end{minipage}
% \end{figure*}
% \begin{figure}
\subsubsection{Problem of Random Mapping}\label{randomassign}
The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
The average shuffle read time is $3.2\%$ of total reduce completion time.

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{fig/shuffle}
	\caption{Shuffle Data Prediction}
	\label{fig:shuffle}
	\vspace{-1em}
\end{figure}
As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
We then remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
This is because that data skew commonly exists in data-parallel computing \cite{skewtune, reining, gufler2012load}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

@@

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/hash_pre}
		\caption{Linear Regression Prediction of Hash Partitioner\newline}
		\label{fig:hash_pre}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
		\label{fig:range_pre_sample}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	\vspace{-1em}
\end{figure*}

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\State\While{$idx <$ len$R$}
			% \Comment{Schedule reduces by MinHeap}
			\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
			\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
			\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
			\State Sift down $M\left[0\right]$ by $size$
			\State $idx\gets idx-1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		% \Comment{$m$ is the number of input data}
		% \Comment{$r$ is partition number of reduces}
		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
		% \Comment{$c$ is $r*m$ array of composition data}
		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.
		\State Return if it is impossible.
		% \State $reduces \gets M\left[reduce.host\_id\right].reduce$	
		% \State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
		% \State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
		% \State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
		% \State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
		% \If{$size\_host\leq upper\_bound$ \textbf{and} \\
		% 	\qquad \; $size\_assigned\leq upper\_bound$}
		% 	\State Swap $candidates$ and $reduce$
		% 	\State Update $size$ in $M$
		% 	\State Update $assigned\_host$ in $candidates$ and $reduce$
		% \EndIf
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node 
and applies the longest processing time rule (LPT) \cite{design} to achieve $4/3\text{-}approximation$ optimum. 
Since the sizes of tasks are considered while scheduling, Heuristic MinHeap can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that Heuristic MinHeap has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
% After the scheduling, the completion time of reduce stage is close to the optimal. \textcolor{red}{may need to add math prove between this and optimal}.
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
% The closer $prob$ is to $1/m$, the more evenly this reduce partition is produced in cluster.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
% We set maximum $upper\_bound$ of performance degradation equals to 10\% that can be traded for locality (in extreme skew scenarios).
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.

\subsubsection{Cope with Multiple Shuffle Dependencies}
% \ifrevision
% \marginpar{E5}
% \fi
A reduce stage can have more than one shuffle dependencies in the current DAG computing frameworks. 
The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
For those pending shuffles, it is impossible to predict their sizes. 
This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
But doing this introduces large overhead such as extra task serialization. 
To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Accumulated Heuristic Scheduling for Multi-Shuffles}
\label{mhminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
		\State $m\gets$ partition number of map tasks
		\Comment \emph{shuffles} are the previous schedule result 
		\ForAll{$r$ in $p\_reduces$}
			\State $r.size \mathrel{+}= \text{\emph{shuffles}}\left[r.rid\right].size$
			\State $new\_prob\gets \text{\emph{shuffles}}\left[r.rid\right].size / r.size$
			\If{$new\_prob\geq r.prob$}
				\State $r.prob\gets new\_prob$
				\State $r.host\_id\gets \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$
			\EndIf
		\EndFor
		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
		\ForAll{$host\_id$ in $M$}
			\Comment Re-shuffle
			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
				\If{$host\neq \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$}
				\State Re-shuffle data to $host$
				\State $\text{\emph{shuffles}}\left[r.rid\right].assigned\_host\gets host$
				\EndIf
			\EndFor
		\EndFor
		\Return $M$
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}
